\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-22 paper/mswp2012-proposal.tex
Try to answer more questions of 'Project goals and deliverables'

\begin{itemize}
	\item \emph{Technology}. 
	The goal of the modern health care system is to use today's possibilities to support a healthier lifestyle.
	\item \emph{Ubiqitous Computing and Usability}.
	The modern health care system should be an easy to use system that transparently integrates into ones living day while staying out of the way and minimizing the need of manual interactions.
	\item \emph{Psychology}.
	The modern health care system should use and gather knowledge on what motivates people to stay in shape, especially in the field of gamification.
\end{itemize}

@@

@@

\subsection{Innovative apsects}
The combination of different aspects already in use like surveillance of old people living alone to achieving the daily goal of walking 1.5 kilometers or drinking 2.5 liters of water is new. In Africa there is a project to do a basic doctor consultation by SMS. The reason for this is because nothing is spread that widely other than a simple mobile phone. Going many kilometers for a checkup to the next doctor is often way to far for people with no car or the possibility to use public transportation. Approaches like this one are already rolled out for certain diseases and specialized groups (see \footnote{\url{http://derstandard.at/1345166647163/Der-Doktor-im-iPhone}}). Combining all the existing programs to one big socialized game for healthier living could even change economy.

>>>>

\begin{itemize}
	\item \emph{Technology}. 
	The goal of the modern health care system is to use today's possibilities to support a healthier lifestyle. Technology is often blamed as a culprit for the increasing number of unhealthy people. We want to use technology to increase the overall health of people. Currently there are several focused approaches that use technology to improve health, see \ref{sect:star}. We want to create a system that does not only track isolated parts of your health-related activities but rather creates a big picture of everything you do and therefore is much more accurate than the existing systems.
	\item \emph{Ubiqitous Computing and Usability}.
	The modern health care system should be an easy to use system that transparently integrates into ones living day while staying out of the way and minimizing the need of manual interactions. The increasing success of mobile computing was a start to a new form of computing ultimately leading to ubiquitous and pervasive computing in the future. Ubiquitous computing is a post-desktop model of human computer interaction and describes the integration of computing into everydays activities. The modern health care system should be a case study on how ubiquitous computing performs on a broader range. 
	\item \emph{Psychology}.
	The modern health care system should use and gather knowledge on what motivates people to stay in shape, especially in the field of gamification. The broad range of data generated by our system should be analyzed and evaluated to generate statistics on how gamification of everydays tasks can improve life. The game designer Jane McGonigal describes her journey from becoming suicidal to enjoying life in her TED talk \emph{The game that can give you 10 extra years of life} \footnote{\url{http://www.ted.com/talks/jane_mcgonigal_the_game_that_can_give_you_10_extra_years_of_life.html}}. She describes how turning her life into a game changed her perception of life and made her a happy person. This and other examples clearly show that gaming can have a very high impact on peoples life, with the help of the modern health care system we want to generate scientific data to prove this.
	\item \emph{Security and Privacy}.
	The increasing trend to an interconnected system and to ubiquitous and pervasive computing leads to higher risks of misuse of data. Health related data is very sensible data and therfore the modern health care system must guarantee data security and privacy from today's point of view. We need to investigate in how communication can stay private and how data can be obsfuscated without loosing the ability to generate useful statistics.
\end{itemize}

@@

The main hyphotesis to be investigated in this project is in the field of usability and ubiquitous computing. We want to generate knowledge on how a tracking system that monitors your whole day can be designed without being noticable and annoying. As already stated such a system can only succeed if the generation of useful data is as automized as possible, manual entries of exercices or nutrition facts can improve the data accuracy but shouldn't be vital for a working system.

The focus of the modern health care system isn't to become a game and therefore to compete with other game approaches like XBox Kinect or the Nintendo Wii. The main goal of these devices is to be a gaming platform, exercising while playing is a secondary factor that is to a great extent used for marketing reasons. Furthermore the modern health care system is no phychological study. The knowledge generated in this area is a side-product and not the main focus and the evaluation of the generated data is not part of the project. We also do not want to create an advertisement platform that can be (ab)used by our partners to spam our users. We do offer targeted ads, but only to a certain extend to be able to gain the interest of more partners in the industry.

@@

\subsection{Innovative aspects}
The combination of different aspects already in use like surveillance of old people living alone to achieving the daily goal of walking 1.5 kilometers or drinking 2.5 liters of water is new. In Africa there is a project to do a basic doctor consultation by SMS. The reason for this is because nothing is spread that widely other than a simple mobile phone. Going many kilometers for a checkup to the next doctor is often way to far for people with no car or the possibility to use public transportation. Approaches like this one are already rolled out for certain diseases and specialized groups (see \footnote{\url{http://derstandard.at/1345166647163/Der-Doktor-im-iPhone}}). Combining all the existing programs to one big socialized game for healthier living could even change economy.
